\chapter{RFD and MRAI correlation}
\label{cha:bgp_rfd}

%\begin{itemize}
%    \item Expose more deeply what is RFD
%    \item Expose previous studies about RFD
%    \item Today RFD? Outdated
%\end{itemize}

\ac{RFD} is another parametr of \ac{BGP} used to avoid messages storms.
It is used to avoid flapping routes to continously make the network unstable.
When a network flaps a certain value is increased and when it overpass a threshold
then the route is suppressed and not advertised anymore until it goes back
below the threshold (ora after a certian time).

\ac{RFD}, other than \ac{MRAI}, is one of the most studied parameters of \ac{BGP}
because of its influence in the convergence time \cite{mao2002route,pelsser2011route}.
\ac{RFD} received different updates from its first implementation, but recent 
studies showed that most of the providers still use outdated parameters  \cite{gray2020bgp}.

The use of deprecated values can lead to a to havy restrictive suppression
of small routes delaying the correct spreading of information.
Some cases of suppression are caused by faulty interfaces that haviliy flaps hundreds of times, 
while other times is just an update of the node configuration that
cause the route to flaps a couple of times and still be suppressed.

In the following chapters I am going to show how legacy \ac{RFD} can affect 
small flapss and how would the new versione of \ac{RFD} reacted to it.
Finally, I would look forward to understand the correlation between \ac{RFD}
and \ac{MRAI}.
When a suppressed route is shared again it could provoke messages storm that
triggers different \ac{MRAI} session, or the opposite case, a low \ac{MRAI} that
cause the grow of the figure of merit that suppress a route.

\section{RFD on toy topologies}
\label{sec:bgp_rfd_toy}

\begin{itemize}
    \item What is the impact of RFD?
    \item In which occasion is present RFD?
    \item Clique
    \item Variations thanks to MRAI
\end{itemize}

\section{RFC 2439 VS RFC 7196}
\label{sec:bgp_rfd_comparison}

\begin{itemize}
    \item Time comparison between both of them
    \item how them react differently?
    \item why?
\end{itemize}

\section{Mice VS Elephants}
\label{sec:bgp_rfd_mice_vs_elephants}

\begin{itemize}
    \item What is Mice VS Elephants?
    \item How has been studied in the past?
    \item Introduce how MRAI affects mice VS elephants
\end{itemize}
